### 2016-12-13 results.tex
continuing my pass...

\medskip
\algorithmv{$\Qry(\pubaux,\privaux,q_x)$}\\
$M\gets\pubaux$, $K \gets \privaux$\\
for $j \in \{1,2,\ldots,k\}$\\
\nudge $h_j \gets F_{K}(\langle j,x \rangle) $\\
\nudge if $M[h_j] \neq 1$ then Return 0\\
Return 1 } \caption{{\bf Left:} $\Rep$ and $\Qry$ algorithms for
classical Bloom
  filter $\setprim_{\mathrm{Bloom}}$ in the ROM for a hash function $H\colon \mathbb{N} \times
  \elts \to [m]$, where $|S| \leq n$. {\bf Right:} $\Rep$ and $\Qry$
  algorithms for the domain-separated PRF data structure
  $\setprim_{\mathrm{ds}}$, using function family $F \colon
  \calK \times \elts \to [m]$.  Both constructions have query set is $\calQ=\{q_x\colon
  \univ \to \bits\}$ where $q_x(S)=1 \Leftrightarrow x \in S$.  }
\label{fig:bf-and-ds}
\end{figure}

\subsection{Classical Bloom Filter in the Random-Oracle Model}
Fix $k,m,n \geq 0$ and a universe $\elts$.  Then the classical Bloom
filter set-membership data structure $\setprim_{\mathrm{Bloom}}=
(\Rep, \Qry)$ over~$\elts$ is defined as in
Figure~\ref{fig:bf-and-ds} (left side) for sets $S \subseteq \elts$
of size at most $|S|\leq n$. We define~$\setprim_{\mathrm{Bloom}}$
in the random-oracle model (ROM), as the traditional analysis of
correctness (as a function of $n,k,m$) is done in this
model.\footnote{The standard-model version would have $\Rep$ choose
$H_1,\ldots,H_k$ from some function family, compute $h_j$ using
these, and place their description in $\pubaux$.}

@@

\begin{theorem}\label{thm3}\label{thm:bf-correctness}
Fix $k,m,n,r>0$ and~$\elts$, and let $\setprim_{\mathrm{Bloom}}=
(\Rep, \Qry)$ be the classical Bloom filter (set-membership) data
structure over~$\elts$. For any adversary~$A$ that makes a total
of~$q_T$ queries to the $\Test$ oracle, $q_R$ queries to the random
oracle, and has time-complexity~$O(t)$,
\[
\AdvCorrect{\setprim_{\mathrm{Bloom}},r}{A} \leq  {\dbinom{q_T + q_H-1}{r-1}} \left( (1-e^{-kn/m})^k + O(1/n) \right)^r\,.
\]
\end{theorem}
Kirsch and Mitzenmacher~\cite{kirsch2006less} show that the ($r=1$,
zero-query) error-probability
for~$\setprim_\mathrm{Bloom}$ is %always within $O(1/n)$ of
$(1-e^{-kn/m})^k+O(1/n)$. %, although the asymptotic rate of
%convergence is faster than~$1/n$.
The multiplicative %(``hybrid'')
term arises as a result of moving from the zero-query to the
adaptive setting. Also note that $\binom{q_T+q_H-1}{r-1} \leq
(eq/r)^r$ (letting $q=q_T+q_H$, and assuming $q\gg r$), in which
case the bound becomes
\[\left(eq/r \cdot (1-e^{-kn/m})^k + O(q/rn) \right)^r.\]
Loosely, and ignoring the low-order term, this is the bound expected
by viewing the attacker as trying to find an error in each of~$r$
independent``rounds,'' each round consisting of~$q/r$ attempts.
\jnote{I didn't find the last two sentences helpful.}
%JK
\input{BF_correctness}

\heading{Privacy. }
Turning to privacy, we observe immediately that the classical BF, in the
ROM, does not meet our SS-privacy notion when the leakage function
fails to reveal the entire set~$S$.  This is because the set~$S$ is
adversarially chosen, and the adversary has access to the random
oracle, i.e. the hash functions used to make~$\pubaux$.  Thus the
adversary can simply check that the $\pubaux$ it receives is correct.
Thus, unless $m,k,n$ are such that the false-positive rate is large,
the simulator needs to call the random oracle on the points in~$S$ in order to ``fool'' the adversary.
%\tsnote{I'm still not completely comfortable with this.  It isn't explicit in our SS notion, but I assume that~$A$ is stateful and so knows~$S$ in its second stage?  If so, I wonder if the classic BF in the ROM would be secure relative to a weaker notion (but still stronger than OW) in which the second stage does not know~$S$?  This seems likely to me.}

We note that this will be true for \emph{any} data structure that returns an empty $\privaux$, because this implies that $\pubaux$ alone suffices to evaluate $\Qry(\pubaux,\privaux,\cdot)$.

\begin{theorem}[{\rm OW-privacy of classic BF in the ROM}]\label{thm3}\label{thm:bf-ow}
Fix $k,m,n,r>0$, a set~$\elts$, and let $\setprim_{\mathrm{Bloom}}= (\Rep, \Qry)$ be the classical Bloom filter data structure over~$\elts$. Let $\distr{}{}$ be a distribution over subsets of universe~$\univ=2^\elts$, where $\mu = H_\infty(\distr{}{})$.  For any adversary~$A$ that makes $q$~queries to its oracle
\[
\AdvPrivOW{\setprim_{\mathrm{Bloom}},\distr{}{},r}{A} \leq  \frac{(kqn+n)}{2^{\mu}}\;.
\]
\end{theorem}
The straightforward proof will appear in the full version.
Loosely, the $kqn/2^{\mu}$ term arises from the chance that random-oracle queries reveal an element of~$S$ (by the random oracle having
been called on them in the execution of~$\Rep$), and the $n/2^\mu$
term arises to simple guessing of an element of~$S$ should none of the
random-oracle queries reveal an element of~$S$.

@@

\subsection{Domain-Separated PRF-Hash}
Next we consider a natural, secret-key variant of the classic Bloom
filter.  Here the (private) hash functions are instantiated via
$H(j,x)=F_K(\langle j,x\rangle)$, using domain-separation to turn a
PRF (with one secret key) into, effectively, multiple functions that
are computationally indistinguishable from random.  We call this the
domain-separated PRF-hash data structure.

%\heading{Construction of PRF with domain separation.}
\heading{Correctness. } Let $\setprim_{\mathrm{ds}}= (\Rep, \Qry)$
be the set-membership data structure defined on the right-hand side
of Figure~\ref{fig:bf-and-ds}. As in the preceding theorem, the
following says (informally) that if~$F$ is a secure PRF, then this
domain-separated PRF construction is correct against adaptive
adversaries.

@@

\begin{theorem}[{\rm Correctness of DS-PRF}]\label{thm2}\label{thm:ds-correctness}
Fix $k,m,n,r>0$, a set~$\elts$, and let $\setprim_{\mathrm{ds}}= (\Rep, \Qry)$ be the set-membership data structure (over~$\elts$) in Figure~\ref{fig:bf-and-ds}.  For any adversary~$A$ that makes a total of~$q$ queries to its oracle and has time-complexity~$O(t)$, there exists a prf-adversary ~$B$ (explicitly constructed in the proof of this theorem) such that
\[
\AdvCorrect{\setprim_{\mathrm{ds}},r}{A} \leq  \AdvPRF{F}{B}  + {\dbinom{q}{r}} \left( (1-e^{-kn/m})^k + O(1/n) \right)^r\,.
\]
Here, $B$ asks $q$ queries, and has time complexity $O(t+qm)$.
\end{theorem}
We note that Kirsch and Mitzenmacher~\cite{kirsch2006less} show
that the ($r=1$, zero-query) error-probability for~$\setprim_\mathrm{ds}$ is
always within $O(1/n)$ of $(1-e^{-kn/m})^k$, although the asymptotic
rate of convergence is faster than~$1/n$.   As before, the multiplicative term $\binom{q}{r}$ arises when switching from the adaptive to zero-query settings.
\input{ds-correctness}

\heading{Privacy. }
The privacy of $\setprim_{\mathrm{ds}}$ follows directly from our general result, Theorem~\ref{thm:priv-ss}.
\begin{theorem}[\rm{SS-privacy of DS PRF}]\label{thm:ds-ss}
Fix $k,m,n>0$, a set~$\elts$, and let $\setprim_{\mathrm{ds}}= (\Rep,
\Qry)$ be the set-membership data structure described in
Figure~\ref{fig:bf-and-ds}.  For any set~$S \in 2^\elts$, let
$\leak(S)=|S|$.  There exists a simulator~$\Sim$ and adversary~$B$
(making~$kn$ queries) such that, for any adversary~$A$
\[
\AdvPrivSS{\setprim_{\mathrm{ds}},\leak}{A,\Sim} \leq  \AdvPRF{F}{B}\,.
\]
%(Both~$B$ and~$\Sim$ are explicitly constructed in the proof of this theorem.)
\end{theorem}
\begin{proof}
It suffices to give the decomposition of $\Rep$ in to $\Rep_1$ and $\Rep_2$ as required by Theorem~\ref{thm:priv-ss}.
On input a set of distinct elements $S=\{x_1,x_2,\ldots,x_n\}$, algorithm~$\Rep_1$ returns $s_1=\langle 1,x_1 \rangle, s_2=\langle 2,x_1 \rangle, \ldots, s_k\langle k,x_1\rangle, s_{k+1}=\langle 1,x_2\rangle, \ldots,\linebreak s_{2k}=\langle k,x_2\rangle, \ldots ,s_{kn+1}=\langle 1,x_n\rangle, \ldots, s_{kn}=\langle k,x_n \rangle$.  On input $n,F_K(s_1),\ldots,\linebreak F_K(s_{kn})$, algorithm $\Rep_2$ simply initializes an all-zero array~$M$ of~$m$-bits, and sets the positions $M[F_K(s_i)]$ to 1.  It returns~$M$ as $\pubaux$. \hfill\qed
\end{proof}

@@

\subsection{Linear PRF-hash Bloom Filter }
%\heading{Linear-PRF construction. }
The domain-separated PRF-hash requires~$k$ PRF evaluations per set-membership query, and this may be unattractive in certain use cases.  Kirsch and Mitzenmacher~\cite{kirsch2006less} have shown that two PRF evaluations suffices, defining the hash functions to be $h_i(x)=F_K(\langle 1,x \rangle) + j\cdot F_K(\langle 2,x \rangle) \bmod m$, where~$m$ is the bit-length of the Bloom filter.\footnote{Actually, they define $h_i(x)=F_{K_1}(x)  + j\cdot F_{K_2}(x) \bmod m$, using distinct keys instead of domain-separation, but the constructions are equivalent with respect to security.} We call this the \emph{linear PRF-hash} Bloom Filter.  In this section, we show that this scheme is both correct and private with respect to our SS notion.

@@

Taken together, the results of this section and the next highlight how sensitive the privacy of linear PRF-hash constructions is to usage.

@@

%%%%%%%%%%%%%%%%% BIGRAM LINEAR-PRF (AKA "NIEDERMEYER")  %%%%%%%%%%%%%%%%%%%%
\subsection{Bigram Linear-PRF Construction}
%\heading{Bigram Linear-PRF construction (``Niedermeyer''). }
%\heading{Correctness.}
%\todo{Correctness theorem for this scheme.  Should follow pretty closely the one for ``plain'' linear-PRF.}\tsnote{Actually not sure this is that interesting, but for parallel structure one would want to give it.}
\heading{Privacy. }
Consider the set-membership data structure given in Figure~\ref{fig:lin-and-bi-lin} (right side), which we call the \emph{bigram linear-PRF} construction.  This construction is of practical interest, as it has been suggested as a way to address the privacy-preserving record-linkage problem, in particular for linking common records in medical databases~\cite{niedermeyer2014cryptanalysis,schnell2011novel}.
We only address the privacy of this construction, as the correctness
follows immediately from the correctness of the Linear-PRF
construction.  The privacy, however, does not.  Here we exhibit an
efficient SS-privacy attack even when simulator is provided nearly the
entire set.  Consider the following ``all-but-last'' leakage function.
On input a set~$S=\{x_1,x_2,\ldots,x_n\}$, it assigns $x'_n \gets
x_n[1:|x_n|-1]$ and returns
$\mathsf{leak_{abl}}(S)=\{x_1,x_2,\ldots,x'_n\}$.

@@

On the other hand, we can show that this data structure \emph{is}
semantically secure with respect to a different leakage function,
namely, one that leaks the sizes of the intersections of the various
bigram sets. Specifically, for a set $S$ define ${\sf leak}_\cap(S)$
via the following algorithm:

@@

\begin{figure}[tp]
\centering
\hfpagess{.45}{.45}
{
\adversaryv{$A_{\mathrm{ss}}^{\TestOracle,H}(\pubaux)$}\\[1ex]
$M \gets \pubaux$\\
for $\ell=1$ to $\binom{m}{k}$\\
\nudge $i_1,i_2,\ldots,i_k \gets \mathcal{I}_\ell$\\
\nudge $x \gets M[i_1] \xor M[i_2] \xor \cdots \xor M[i_k]$\\
\nudge if  $x \not\in S \wedge \left(\bigwedge_{j=1}^k H(j,x)=i_j \right)$ then \\
\nudge\nudge $a\gets\TestOracle(x)$\\
\nudge\nudge Return $\bot$\\
}
{
\adversaryv{$A_{\mathrm{ow}}^{H}(\pubaux)$}\\[1ex]
$M \gets \pubaux$\\
for $x \in X_1,X_2,\ldots,X_{q-1}$\\
\nudge for $j=1$ to $k$ \\
\nudge \nudge \nudge $i_j \gets H(j,x)$\\
\nudge $x' \gets M[i_1] \xor M[i_2] \xor \cdots \xor M[i_k]$\\
\nudge if $x' = x$ then Return $x$\\
Return~$X_{q}$
}
%{
%\adversaryv{$A^{\TestOracle}(\pubaux)$}\\[1ex]
%$M \gets \pubaux$\\
%for $1 \leq i_1 < i_2 < \cdots < i_k \leq m$\\
%\nudge $x \gets M[i_1] \xor M[i_2] \xor \cdots \xor M[i_k]$\\
%\nudge if $\TestOracle(x)=1$ then Return $\bot$
%}
%\caption{Adversary for Theorem~\ref{thm:xxx}.  \textbf{Left:} public hash case, \textbf{Right:} private hash case.}
\caption{{\bf Left:} Correctness attack for garbled Bloom filters with public~$M$.  The sequence $\mathcal{I}_1,\mathcal{I}_2,\ldots$ is some implicit enumeration of~$k$-tuples of indices over $[m]$.
{\bf Right:} One-wayness attack for garbled Bloom filters with public~$M$.  The sequence $X_1,X_2,\ldots,X_q,$ are the~$q$ most probable points in the support of~$\distr{}{}$ in decreasing order.  }
\label{fig:adv-gbf}
\end{figure}
Dong, Chen and Wen~\cite{dong2013private} introduce a set-membership data
structure called a \emph{garbled Bloom filter} (GBF).   Modulo some implementation
details, a GBF is like a classical Bloom filter, but
rather than storing a bit 1 at the indices determined by $H_j(x)$, the
GBF stores xor-shares of~$x$.  Thus, if $x \in S$, then hashing~$x$
and xoring together the strings stored at the indicated positions
recovers~$x$. We give the pseudocode for the GBF $\Rep$ and $\Qry$
algorithms in Figure~\ref{fig:gbf}.

@@

Consider the adversary described in the left half of Figure~\ref{fig:adv-gbf}.  In one
round of the for-loop, it pics~$k$ positions $i_1,i_2,\ldots,i_k$, and
xors the strings at these positions to get a candidate~$x$.   If $x
\in S$, which the adversary knows in the correctness experiment, then
it moves on to a new set of positions.  If $x \not\in S$ and
$h_{1}(x)=i_1 \wedge h_2(x)=i_2 \wedge \cdots \wedge h_k(x) = i_k$,
then it \emph{must be} that $x$ is a false-positive.   Indeed, note
that the probability of this (in the ROM) is precisely the
false-positive rate of a classical BF using the same $(k,m,n)$ as the GBF.

>>>>

\medskip
\algorithmv{$\Qry(\pubaux,\privaux,q_x)$}\\
$M\gets\pubaux$, $K \gets \privaux$\\
for $j \in \{1,2,\ldots,k\}$\\
\nudge $h_j \gets F_{K}(\langle j,x \rangle) $\\
\nudge if $M[h_j] \neq 1$ then Return 0\\
Return 1 } \caption{{\bf Left:} $\Rep$ and $\Qry$ algorithms for the
classical Bloom
  filter $\setprim_{\mathrm{Bloom}}$ in the ROM for a hash function $H\colon \mathbb{N} \times
  \elts \to [m]$, where $|S| \leq n$. \jnote{Both should abort if $|S|>n$.}
  {\bf Right:} $\Rep$ and $\Qry$
  algorithms for the domain-separated PRF data structure
  $\setprim_{\mathrm{ds}}$, using function family $F \colon
  \calK \times \elts \to [m]$.  Both constructions have query set $\calQ=\{q_x\colon
  \univ \to \bits\}$ where $q_x(S)=1 \Leftrightarrow x \in S$.  }
\label{fig:bf-and-ds}
\end{figure}

\subsection{Classical Bloom Filter in the Random-Oracle Model}
Fix $k,m,n \geq 0$ and a universe $\elts$.  Then the classical Bloom
filter set-membership data structure $\setprim_{\mathrm{Bloom}}=
(\Rep, \Qry)$ over~$\elts$ is defined as in
Figure~\ref{fig:bf-and-ds} (left side) for sets $S \subseteq \elts$
of size at most $|S|\leq n$. \jnote{This should really be
parameterized everywhere, e.g., as
$\setprim_{\mathrm{Bloom}}^{k,m,n}$.} We
define~$\setprim_{\mathrm{Bloom}}$ in the random-oracle model (ROM),
as the traditional analysis of correctness (as a function of
$n,k,m$) is done in this model.\footnote{The standard-model version
would have $\Rep$ choose $H_1,\ldots,H_k$ from some function family,
compute $h_j$ using these, and place their description in
$\pubaux$.}

@@

\jnote{We should state the bound in the theorem in terms of resource
bounds , rather than in terms of a fixed adversary~$A$ (i.e., bound
$\Pi_{\mathrm{Bloom},r}(t,q_T, q_H)$ not
$\Pi_{\mathrm{Bloom},r}(A)$---note we need to define the former in
the ROM in Section~3). Same goes for all theorems.}

\begin{theorem}\label{thm3}\label{thm:bf-correctness}
Fix $k,m,n,r>0$ and~$\elts$, and let $\setprim_{\mathrm{Bloom}}=
(\Rep, \Qry)$ be the classical Bloom filter (set-membership) data
structure over~$\elts$. For any adversary~$A$ that makes a total
of~$q_T$ queries to the $\Test$ oracle, $q_R$ queries to the random
oracle, and has time-complexity~$O(t)$,
\[
\AdvCorrect{\setprim_{\mathrm{Bloom}},r}{A} \leq  {\dbinom{q_T + q_H}{r}} \left( (1-e^{-kn/m})^k + O(1/n) \right)^r\,.
\]
\end{theorem}
Note that Kirsch and Mitzenmacher~\cite{kirsch2006less} show that
the ($r=1$, zero-query) error-probability
for~$\setprim_\mathrm{Bloom}$ is %always within $O(1/n)$ of
$(1-e^{-kn/m})^k+O(1/n)$, though the asymptotic rate of convergence
is faster than~$1/n$.
The multiplicative %(``hybrid'')
term is due to moving from the zero-query to the adaptive setting.
Also note that $\binom{q_T+q_H}{r} \leq (eq/r)^r$ (letting
$q=q_T+q_H$), in which case the bound becomes
\[\left(eq/r \cdot (1-e^{-kn/m})^k + O(q/rn) \right)^r.\]
Loosely, and ignoring the low-order term, this is the bound expected
by viewing the attacker as trying to find an error in each of~$r$
independent``rounds,'' each round consisting of~$q/r$ attempts.
\jnote{I didn't find the last two sentences helpful.}
\input{BF_correctness}

\heading{Privacy. } We observe that, intuitively, the classical
Bloom filter does not meet our simulation-based privacy notion
except in trivial cases (e.g., if the leakage function reveals the
entire set, the false-positive rate is~1, or the attacker makes no
$H$-queries). This is because the attacker knows the set~$S$; as
long as the attacker can compute~$H$ (as it can in the ROM), it can
simply check that the $\pubaux$ it receives is consistent with~$S$.
%\tsnote{I'm still not completely comfortable with this.  It isn't explicit in our SS notion, but I assume that~$A$ is stateful and so knows~$S$ in its second stage?  If so, I wonder if the classic BF in the ROM would be secure relative to a weaker notion (but still stronger than OW) in which the second stage does not know~$S$?  This seems likely to me.}
We note that this will be true for \emph{any} data structure for
which $\privaux$ is empty, since in that case $\pubaux$ alone
suffices to evaluate $\Qry(\pubaux,\privaux,\cdot)$. \jnote{In the
ROM the attack requires that the attacker can query the ROM
sufficiently many times.}

On the other hand, we can show that the classical Bloom filter does
meet our notion of one-wayness in the~ROM:

\begin{theorem}%[{\rm OW-privacy of classic BF in the ROM}]
%\label{thm3}
\label{thm:bf-ow} Fix $k,m,n>0$ and~$\elts$, and let
$\setprim_{\mathrm{Bloom}}= (\Rep, \Qry)$ be the classical Bloom
filter data structure over~$\elts$. Let $\distr{}{}$ be a
distribution over subsets of $\elts$ of size at most~$n$, and let
$\mu = H_\infty(\distr{}{})$. Then for any adversary~$A$ that makes
at most $q_H$~queries to~$H$,
\[
\AdvPrivOW{\setprim_{\mathrm{Bloom}},\distr{}{}}{A} \leq  \frac{(kq_H n+n)}{2^{\mu}}\;.
\]
\end{theorem}
\jnote{I don't see how you get the above bound. A gross upper bound
is obtained by saying that the attacker wins if it ever makes a
single query $H(\star, x)$ with $x \in S$. The probability of that
is $q_H/2^\mu$, which is better than $kq_Hn/2^\mu$.} The
straightforward proof will appear in the full version. Roughly, the
$kqn/2^{\mu}$ term \jnote{Revisit later.} arises from the event that
random-oracle queries reveal an element of~$S$, and the $n/2^\mu$
term represents the probability that the attacker simply guesses an
element of~$S$.

@@

\subsection{A Secret-Key Variant of the Bloom Filter}
Next we consider a natural, secret-key variant of the classical
Bloom filter where the (private) hash functions are instantiated via
$H(j,x)=F_K(\langle j,x\rangle)$, where $F$ is a pseudorandom
function (PRF), using domain separation to turn a PRF into,
effectively, multiple (independent) random functions. (Refer to the
right side of Figure~\ref{fig:bf-and-ds}.) We call this the
\emph{domain-separated PRF data structure}.

\jnote{Maybe just call it ``pseudorandom hash''?}

%\heading{Construction of PRF with domain separation.}
\heading{Correctness. } As in Theorem~\ref{thm3}, the following says
(informally) that if~$F$ is a PRF, then the domain-separated PRF
construction enjoys correct against adaptive adversaries.

@@

\jnote{As with the classical BF, this should always be
parameterized, e.g., as $\setprim_{\mathrm{ds}}^{k,m,n}(F)$.}

\begin{theorem}%[{\rm Correctness of DS-PRF}]
\label{thm2}\label{thm:ds-correctness} Fix $k,m,n,r>0$ and~$\elts$,
and let $\setprim_{\mathrm{ds}}= (\Rep, \Qry)$ be the
domain-separated PRF data structure over $\elts$. Then
\[
\AdvCorrect{\setprim_{\mathrm{ds}},r}{t, q_T} \leq  \AdvPRF{F}{O(t+q_T m), q_T}  + {\dbinom{q_T}{r}} \cdot \left( (1-e^{-kn/m})^k + O(1/n) \right)^r\,.
\]
\end{theorem}
\jnote{I don't think we ever define $\AdvPRF{F}{q, t}$.}

%We note that Kirsch and Mitzenmacher~\cite{kirsch2006less} show
%that the ($r=1$, zero-query) error-probability for~$\setprim_\mathrm{ds}$ is
%always within $O(1/n)$ of $(1-e^{-kn/m})^k$, although the asymptotic
%rate of convergence is faster than~$1/n$.   As before, the multiplicative term $\binom{q}{r}$ arises when switching from the adaptive to zero-query settings.
\jnote{The proof of this theorem should be ``morally the same'' as
the proof of Theorem~\ref{thm3} (unless I am missing some
subtlety?). So I think we should omit this proof altogether. If not,
then it should follow the same structure as the proof of
Theorem~\ref{thm3} or else the reader is likely to be confused (as I
was).}

\input{ds-correctness}

\heading{Privacy. } In contrast to the case of classical Bloom
filters (with public hash functions), the domain-separated PRF data
structure achieves our simulation-based notion of privacy. Indeed,
this follows directly from Theorem~\ref{thm:priv-ss}.

\begin{theorem}%[\rm{SS-privacy of DS PRF}]
\label{thm:ds-ss} Fix $k,m,n>0$ and ~$\elts$, and let
$\setprim_{\mathrm{ds}}= (\Rep, \Qry)$ be the domain-separated PRF
data structure.  Let $\leak(S)=|S|$. Then
\[
\AdvPrivSS{\setprim_{\mathrm{ds}},\leak}{A,\Sim} \leq
\AdvPRF{F}{B}\,.
\]
%(Both~$B$ and~$\Sim$ are explicitly constructed in the proof of this theorem.)
\end{theorem}
\begin{proof}
Let $\ell(n) = kn$. Let $\Rep_1$ be the algorithm that, on input a
set $S=\{x_1,\ldots,x_n\}$, outputs $\{\langle i,x_j \rangle\}_{i\in
{k}, j \in [n]}$. Let $\Rep_2$ be the algorithm that, on input
$n,y_1, \ldots, y_{\ell(n)}$, initializes an $m$-bit array $M$ to~0
and then sets $M[y_i] \gets 1$ for $i \in [\ell(n)]$. One can easily
verify that $(\Rep_1, \Rep_2, \ell, F)$ is a factoring of~$\Pi$.
Applying Theorem~\ref{thm:priv-ss} yields the claimed result.
\hfill\qed
\end{proof}

@@

%JK
\subsection{Linear PRF-hash Bloom Filter }
%\heading{Linear-PRF construction. }
The domain-separated PRF-hash requires~$k$ PRF evaluations per
set-membership query, and this may be unattractive in certain use
cases.  Kirsch and Mitzenmacher~\cite{kirsch2006less} have shown
that two PRF evaluations suffice, defining the hash functions to be
$h_i(x)=F_K(\langle 1,x \rangle) + j\cdot F_K(\langle 2,x \rangle)
\bmod m$, where~$m$ is the bit-length of the Bloom
filter.\footnote{Actually, they define $h_i(x)=F_{K_1}(x)  + j\cdot
F_{K_2}(x) \bmod m$, using distinct keys instead of
domain-separation, but the constructions are equivalent with respect
to security.} We call this the \emph{linear PRF-hash} Bloom filter.
\jnote{Maybe call it ``Pairwise-independent hash''?} In this
section, we show that this scheme is both correct and private.

@@

Taken together, the results of this section and the next highlight
the privacy of the linear PRF-hash construction can be sensitive to
its usage.

@@

%%%%%%%%%%%%%%%%% BIGRAM LINEAR-PRF (AKA "NIEDERMEYER")  %%%%%%%%%%%%%%%%%%%%
\subsection{Bigram Linear-PRF Construction}
%\heading{Bigram Linear-PRF construction (``Niedermeyer''). }
%\heading{Correctness.}
%\todo{Correctness theorem for this scheme.  Should follow pretty closely the one for ``plain'' linear-PRF.}\tsnote{Actually not sure this is that interesting, but for parallel structure one would want to give it.}
\heading{Privacy. } Consider the set-membership data structure given
in Figure~\ref{fig:lin-and-bi-lin} (right side), which we call the
\emph{bigram linear-PRF} construction.  This construction is of
practical interest, as it has been suggested as a way to address the
privacy-preserving record-linkage problem, in particular for linking
common records in medical
databases~\cite{niedermeyer2014cryptanalysis}. %,schnell2011novel}.
We only address the privacy of this construction, as the correctness
follows immediately from the correctness of the Linear-PRF
construction.  The privacy, however, does not.  Here we exhibit an
efficient SS-privacy attack even when simulator is provided nearly
the entire set.  Consider the following ``all-but-last'' leakage
function. On input a set~$S=\{x_1,x_2,\ldots,x_n\}$, it assigns
$x'_n \gets x_n[1:|x_n|-1]$ and returns
$\mathsf{leak_{abl}}(S)=\{x_1,x_2,\ldots,x'_n\}$.

@@

On the other hand, we can show that this data structure \emph{is}
secure with respect to a different leakage function, namely, one
that leaks the sizes of the intersections of the various bigram
sets. Specifically, for a set $S$ define ${\sf leak}_\cap(S)$ via
the following algorithm:

@@

\begin{figure}[tp]
\centering
\hfpagess{.45}{.45}
{
\adversaryv{$A_{\mathrm{ss}}^{\TestOracle,H}(\pubaux)$}\\[1ex]
$M \gets \pubaux$\\
for $\ell=1$ to $\binom{m}{k}$\\
\nudge $i_1,i_2,\ldots,i_k \gets \mathcal{I}_\ell$\\
\nudge $x \gets M[i_1] \xor M[i_2] \xor \cdots \xor M[i_k]$\\
\nudge if  $x \not\in S \wedge \left(\bigwedge_{j=1}^k H(j,x)=i_j \right)$ then \\
\nudge\nudge $a\gets\TestOracle(x)$\\
\nudge\nudge Return $\bot$\\
}
{
\adversaryv{$A_{\mathrm{ow}}^{H}(\pubaux)$}\\[1ex]
$M \gets \pubaux$\\
for $x \in X_1,X_2,\ldots,X_{q-1}$\\
\nudge for $j=1$ to $k$ \\
\nudge \nudge \nudge $i_j \gets H(j,x)$\\
\nudge $x' \gets M[i_1] \xor M[i_2] \xor \cdots \xor M[i_k]$\\
\nudge if $x' = x$ then Return $x$\\
Return~$X_{q}$
}
%{
%\adversaryv{$A^{\TestOracle}(\pubaux)$}\\[1ex]
%$M \gets \pubaux$\\
%for $1 \leq i_1 < i_2 < \cdots < i_k \leq m$\\
%\nudge $x \gets M[i_1] \xor M[i_2] \xor \cdots \xor M[i_k]$\\
%\nudge if $\TestOracle(x)=1$ then Return $\bot$
%}
%\caption{Adversary for Theorem~\ref{thm:xxx}.  \textbf{Left:} public hash case, \textbf{Right:} private hash case.}
\caption{{\bf Left:} Correctness attack for garbled Bloom filters with public~$M$.  The sequence $\mathcal{I}_1,\mathcal{I}_2,\ldots$ is some implicit enumeration of~$k$-tuples of indices over $[m]$.
{\bf Right:} One-wayness attack for garbled Bloom filters with public~$M$.  The sequence $X_1,X_2,\ldots,X_q,$ are the~$q$ most probable points in the support of~$\distr{}{}$ in decreasing order.  }
\label{fig:adv-gbf}
\end{figure}
Dong, Chen and Wen~\cite{CCS:DonCheWen13} introduce a set-membership
data structure called a \emph{garbled Bloom filter} (GBF).   Modulo
some implementation details, a GBF is like a classical Bloom filter,
but rather than storing a bit 1 at the indices determined by
$H_j(x)$, the GBF stores xor-shares of~$x$.  Thus, if $x \in S$,
then hashing~$x$ and xoring together the strings stored at the
indicated positions recovers~$x$. We give the pseudocode for the GBF
$\Rep$ and $\Qry$ algorithms in Figure~\ref{fig:gbf}.

@@

Consider the adversary described in the left half of
Figure~\ref{fig:adv-gbf}.  In one round of the for-loop, it pics~$k$
positions $i_1,i_2,\ldots,i_k$, and xors the strings at these
positions to get a candidate~$x$.   If $x \in S$, which the
adversary knows in the correctness experiment, then it moves on to a
new set of positions.  If $x \not\in S$ and $h_{1}(x)=i_1 \wedge
h_2(x)=i_2 \wedge \cdots \wedge h_k(x) = i_k$, then it \emph{must
be} that $x$ is a false-positive.   Indeed, note that the
probability of this (in the ROM) is precisely the false-positive
rate of a classical Bloom filter using the same $(k,m,n)$ as the
GBF.
